### 2025-03-18 project1/nsSurvey.tex
12

The standard nested simulation procedure is computationally expensive with a wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario.
Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using inner replications from other outer scenarios.
This is referred to as pooling.
Different methods pool inner replications differently, using either a trained supervised learning metamodel or predefined likelihood ratio weights.
\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
For certain risk measures,~\cite{broadie2015risk} show that it’s optimal to allocate the entire simulation budget to outer-level simulations, keeping only 1 inner replication in each outer scenario.
Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios, respectively.
In simulation studies, this approach—using a model of a simulation—is called metamodeling, and such models are termed metamodels~\citep{barton1998simulation}.
Another line of research is a multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.

>>>>

The standard nested simulation procedure is computationally expensive with a wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario.
Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using inner replications from other outer scenarios.
This is referred to as pooling.
Different methods pool inner replications differently, using either a trained supervised learning metamodel or predefined likelihood ratio weights.
\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression metamodel to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
For certain risk measures,~\cite{broadie2015risk} show that it's optimal to allocate the entire simulation budget to outer-level simulations, keeping only 1 inner replication in each outer scenario.
Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression (KRR) model as metamodels to pool the inner replications from all outer scenarios, respectively.
In simulation studies, this approach—using a model of a simulation—is called metamodeling, and such models are termed metamodels~\citep{barton1998simulation}.
Another line of research is a multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.
